---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# missingtool

<!-- badges: start -->
<!-- badges: end -->

The goal of missingtool is to provide a simple way to count missing values across all columns for each level of a grouping variable. It's a convenient wrapper around dplyr's `group_by()` and `summarize()` functions.

## Installation

You can install the development version of missingtool from [GitHub](https://github.com/) with:
``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2025/assignment-b2-juntaic7", ref = "0.1.0")
```

## Example

Here's a basic example using the built-in `airquality` dataset:

```{r example}
library(missingtool)

# Count missing values by Month
count_all_missing_by_group(airquality, Month)

# Using pipe operator
airquality |> count_all_missing_by_group(Month)

# Keep the output grouped
count_all_missing_by_group(airquality, Month, .groups = "keep")
```


